---
title: "Data and scripts for reproduce the analysis contained in the manuscript: 
["A multifaceted approach to analyzing taxonomic, functional, and phylogenetic β diversity"](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1002/ecy.3122)"
author: "Gabriel Nakamura"
date: "01/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Authors

Gabriel Nakamura, Yzel Rondon Súarez, Wagner Vicentin and Leandro Duarte

In this repository you will find all scripts and data needed to reproduce the study performed by [Nakamura et al (2020)](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1002/ecy.3122)

## Repository structure

This repository follow the following structure
```{r rep_str, echo=FALSE}
fs::dir_tree(path = getwd())
```

* analysis_performance: this folder contains all scripts needed to generate simulated metacommunities under all scenarios described in [Nakamura et al. (2020)](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1002/ecy.3122) and test for power and type I error. Additionally, this folder contains a script to test for 
